Coherence between subjective feeling and facial expression: a time-series analysis of human and automatic recognition.

### 2019-04-02 ACII_2019_paper/ACII_2019_word.Rmd
eq
typo

## The link between emotion and facial expression through the behaviorist approach
Based on the behaviorist approach initiated by Darwin in *The Expression of the Emotions in Man and Animals* [@darwin1872expression], facial expression are conceived as a genuine display of individuals inner emotional state. This hypothesis is used as a basis for the Basic Emotion Theory (BET) which states that a set of six emotions are universally displayed and are genetically hardwired not only in humans [@ekman1992argument] but also in different animal species [@de2019mama]. According to this view, "when emotions are aroused by perception of a social event, a set of central commands produce patterned emotion-specific changes in multiple systems, including [...] facial expressions." [@ekman2007directed, p49]. To cope with critics, several amendments have been made to the BET, increasing the number of basic emotions from six to seven  [@ekman1988universality] as well as adding the concept of "display rules" to explain cultural differences in the management of facial expressions [@ekman1987universals]. Even if this theory obtained a popular support, it fails to explain how individuals can feel emotions without expressing them and how individuals can express emotions without feeling them, cases for which display rules cannot be applied to [@kraut1979social, @duran2017coherence].

## The link between emotion and facial expression through the social constructivist approach
Detractors of the Basic Emotion Theory are perceiving emotion not as genetically hardwired but as a learnt association between a given situation and an appropriate response [@averill1980constructivist, @barrett2017emotions]. For the tenants of the constructivist approach, emotions are "concepts" based on past experiences and which are "a collection of embodied, whole brain representations that predict what is about to happen in the sensory environment, what the best action is to deal with impending events, and their consequences for allostasis" [@barrett2017theory, p12]. Following this assumption, faces are used as tools to display signals in social interactions [@crivelli2018facial]. These signals can convey individuals' motivations and readiness [@frijda1997facial] or social messages [@fridlund1995human]. Therefore, facial expressions are thought as behaviors which meaning is inferred by the observer.

@@

$$x_{video_{i}.label_{i}.t_{i}} = \frac{n_{video_{i}.label_{i}.t_{i}}}{n_{video_{i}}}$$

@@

$$x_{video.label.t_{i}} = \frac{n_{video.label.t_{i}}}{n_{video}}$$

>>>>

## The link between emotion and facial expression through the behaviorist approach
Based on the behaviorist approach initiated by Darwin in *The Expression of the Emotions in Man and Animals* [@darwin1872expression], facial expression are conceived as a genuine display of individuals inner emotional state. This hypothesis is used as a basis for the Basic Emotion Theory (BET) which states that a set of six emotions are universally displayed and are genetically hardwired not only in humans [@ekman1992argument] but also in different animal species [@de2019mama]. According to this view, "when emotions are aroused by perception of a social event, a set of central commands produce patterned emotion-specific changes in multiple systems, including [...] facial expressions." [@ekman2007directed, p49]. To cope with critics, several amendments have been made to the BET, increasing the number of basic emotions from six to seven  [@ekman1988universality] as well as adding the concept of "display rules" to explain cultural differences in the management of facial expressions [@ekman1987universals]. Even if this theory obtained a popular support, it fails to explain how individuals can feel emotions without expressing them and how individuals can express emotions without feeling them, cases for which display rules cannot be applied to [@kraut1979social; @duran2017coherence].

## The link between emotion and facial expression through the social constructivist approach
Detractors of the Basic Emotion Theory are perceiving emotion not as genetically hardwired but as a learnt association between a given situation and an appropriate response [@averill1980constructivist; @barrett2017emotions]. For the tenants of the constructivist approach, emotions are "concepts" based on past experiences and which are "a collection of embodied, whole brain representations that predict what is about to happen in the sensory environment, what the best action is to deal with impending events, and their consequences for allostasis" [@barrett2017theory, p12]. Following this assumption, faces are used as tools to display signals in social interactions [@crivelli2018facial]. These signals can convey individuals' motivations and readiness [@frijda1997facial] or social messages [@fridlund1995human]. Therefore, facial expressions are thought as behaviors which meaning is inferred by the observer.

@@

$$x_{video_{i}.label_{j}.t_{k}} = \frac{n_{video_{i}.label_{j}.t_{i}}}{n_{video_{k}}}$$

@@

$$label_{video_{i}} = max{\frac{n_{video.label.t_{i}}}{n_{video}}}$$
